Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-08-15 paper.tex
Integrated split results for buffered slices on SSD

\subsubsection{Merge time breakdown}
Figure~\ref{fig:breakdowns-ssd} shows how the total merge time breaks
down to read, write, seek and overhead time for our algorithms. Naive
blocks and naive slices are shown as references. The huge difference
between naive blocks and naive slices is coming from both the seek
time and the write time, which suggests that seeking degrades the
write rate importantly in addition to introducing extra delays.
Clustered reads reduce the seek time and thus the read time very
substantially. Multiple reads almost anihilate the seek time and bring
the read time to a value comparable to naive slices.  The same
behavior is observed on HDD and on SSD, although the effect of seeking
is slightly smaller on SSD, as expected. Read times are consistently
and substantially lower than write times. This may be a result of
reading data using Python's NumPy package, which is more efficient
than using native Python - as is the case with our writes. The
overhead time is small for both Clustered reads and Multiple reads.
\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-ssd.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-ssd.pdf}
    \caption{Clustered reads}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-ssd.pdf}
    \caption{Multiple reads}
  \end{subfigure}
  \caption{Breakdown of total merge times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}

@@

\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-hdd-split.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-ssd-split.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrites/cwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrites/cwrites-breakdown-ssd.pdf}
    \caption{Clustered writes}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-ssd.pdf}
    \caption{Multiple writes}
  \end{subfigure}
  \caption{Breakdown of total split times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd-split}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}

>>>>

\subsubsection{Merge time breakdown}
Figure~\ref{fig:breakdowns-ssd} shows how the total merge time breaks
down to read, write, seek and overhead time for our algorithms. Naive
blocks and naive slices are shown as references. The huge difference
between naive blocks and naive slices is coming from both the seek
time and the write time, which suggests that seeking degrades the
write rate importantly in addition to introducing extra delays.
Clustered reads reduce the seek time and thus the read time very
substantially. Multiple reads almost anihilate the seek time and bring
the read time to a value comparable to naive slices.  The same
behavior is observed on HDD and on SSD, although the effect of seeking
is slightly smaller on SSD, as expected. Read times are consistently
and substantially lower than write times. This may be a result of
discrepancies between disk read and writes rates, or of reading data using Python's NumPy
package, which is more efficient than using native Python - as is the
case with our writes. The overhead time is small for both Clustered
reads and Multiple reads.
\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-reads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-reads-breakdown-ssd.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-ssd.pdf}
    \caption{Clustered reads}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-ssd.pdf}
    \caption{Multiple reads}
  \end{subfigure}
  \caption{Breakdown of total merge times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}

@@

\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-writes-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-writes-breakdown-ssd.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrites/cwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrites/cwrites-breakdown-ssd.pdf}
    \caption{Clustered writes}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-ssd.pdf}
    \caption{Multiple writes}
  \end{subfigure}
  \caption{Breakdown of total split times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd-split}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}
